---
title: "R Notebook"
output: html_notebook
---

#mercury data frames
DFfl25miA <- as.data.frame(fl25miA)
DFfl100miA <- as.data.frame(fl100miA)
DFfl25miB <- as.data.frame(fl25miB)
DFfl100miB <- as.data.frame(fl100miB)
DFla25miA <- as.data.frame(la25miAsw)
DFla100miA <- as.data.frame(la100miAsw)
DFla25miBA <- as.data.frame(la25miBAsw)
DFla100miBA <- as.data.frame(la100miBAsw)

#relevant mrip data
landOtimA
landOtimB
landTtimA
landTtimB

```{r}
#isolate species, biomass, landings, per site - FLorida

DFfl25miA$Whole_weight <- as.numeric(DFfl25miA$Whole_weight)
DFfl25miA$TL <- as.numeric(DFfl25miA$TL)

str(DFfl25miA)

mercFL25miA <- DFfl25miA %>% 
  group_by(INTSITE,Species) %>% 
  summarise(n = n(), aveWt = mean(Whole_weight, na.rm = TRUE), 
            aveLt = mean(TL, na.rm = TRUE), aveHg = mean(Hg, na.rm = TRUE))

mercFL25miA 

DFfl100miA$Whole_weight <- as.numeric(DFfl100miA$Whole_weight)
DFfl100miA$TL <- as.numeric(DFfl100miA$TL)

mercFL100miA <- DFfl100miA %>% 
  group_by(INTSITE,Species) %>% 
  summarise(n = n(), aveWt = mean(Whole_weight, na.rm = TRUE), 
            aveLt = mean(TL, na.rm = TRUE), aveHg = mean(Hg, na.rm = TRUE))

mercFL100miA 

DFfl25miB$Whole_weight <- as.numeric(DFfl25miB$Whole_weight)
DFfl25miB$TL <- as.numeric(DFfl25miB$TL)

mercFL25miB <- DFfl25miB %>% 
  group_by(INTSITE,Species) %>% 
  summarise(n = n(), aveWt = mean(Whole_weight, na.rm = TRUE), 
            aveLt = mean(TL, na.rm = TRUE), aveHg = mean(Hg, na.rm = TRUE))

mercFL25miB 

DFfl100miB$Whole_weight <- as.numeric(DFfl100miB$Whole_weight)
DFfl100miB$TL <- as.numeric(DFfl100miB$TL)

mercFL100miB <- DFfl100miB %>% 
  group_by(INTSITE,Species) %>% 
  summarise(n = n(), aveWt = mean(Whole_weight, na.rm = TRUE), 
            aveLt = mean(TL, na.rm = TRUE), aveHg = mean(Hg, na.rm = TRUE))

mercFL100miB 

#MRIP
landTtimA
landTtimB

mripFLa <- landTtimA %>% 
  group_by(INTSITE,common) %>% 
  summarise(n = n(), landings = sum(landing), biomass = sum(wgt_ab1, na.rm = TRUE))
mripFLa

mripFLb <- landTtimB %>% 
  group_by(INTSITE,common) %>% 
  summarise(n = n(), landings = sum(landing), biomass = sum(wgt_ab1, na.rm = TRUE))
mripFLb
```

Add in NOLA

```{r}
str(DFla25miA)

mercLA25miA <- DFla25miA %>% 
  group_by(INTSITE,spName) %>% 
  summarise(n = n(), aveWt = mean(aveWt_g, na.rm = TRUE), 
            aveLt = mean(aveLen_cm, na.rm = TRUE), aveHg = mean(HgResult, na.rm = TRUE))
mercLA25miA 

mercLA100miA <- DFla100miA %>% 
  group_by(INTSITE,spName) %>% 
  summarise(n = n(), aveWt = mean(aveWt_g, na.rm = TRUE), 
            aveLt = mean(aveLen_cm, na.rm = TRUE), aveHg = mean(HgResult, na.rm = TRUE))
mercLA100miA 

mercLA25miBA <- DFla25miBA %>% 
  group_by(INTSITE,spName) %>% 
  summarise(n = n(), aveWt = mean(aveWt_g, na.rm = TRUE), 
            aveLt = mean(aveLen_cm, na.rm = TRUE), aveHg = mean(HgResult, na.rm = TRUE))
mercLA25miBA 

mercLA100miBA <- DFla100miBA %>% 
  group_by(INTSITE,spName) %>% 
  summarise(n = n(), aveWt = mean(aveWt_g, na.rm = TRUE), 
            aveLt = mean(aveLen_cm, na.rm = TRUE), aveHg = mean(HgResult, na.rm = TRUE))
mercLA100miBA 

#MRIP
mripLAa <- landOtimA %>% 
  group_by(INTSITE,common) %>% 
  summarise(n = n(), landings = sum(landing), biomass = sum(wgt_ab1, na.rm = TRUE))
mripLAa

mripLAb <- landOtimB %>% 
  group_by(INTSITE,common) %>% 
  summarise(n = n(), landings = sum(landing), biomass = sum(wgt_ab1, na.rm = TRUE))
mripLAb

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
