---
title: "R Notebook"
output: html_notebook
---
library(dplyr)
library(plyr)

#mercury data frames
DFfl25miA <- as.data.frame(fl25miA)
DFfl100miA <- as.data.frame(fl100miA)
DFfl25miB <- as.data.frame(fl25miB)
DFfl100miB <- as.data.frame(fl100miB)
DFla25miA <- as.data.frame(la25miAsw)
DFla100miA <- as.data.frame(la100miAsw)
DFla25miBA <- as.data.frame(la25miBAsw)
DFla100miBA <- as.data.frame(la100miBAsw)

#relevant mrip data
landOtimA
landOtimB
landTtimA
landTtimB

```{r}
#isolate species, biomass, landings, per site - FLorida

DFfl25miA$Whole_weight <- as.numeric(DFfl25miA$Whole_weight)
DFfl25miA$TL <- as.numeric(DFfl25miA$TL)

str(DFfl25miA)

mercFL25miA <- DFfl25miA %>% 
  group_by(INTSITE,Species) %>% 
  summarise(n = n(), aveWt = mean(Whole_weight, na.rm = TRUE), 
            aveLt = mean(TL, na.rm = TRUE), aveHg = mean(Hg, na.rm = TRUE))

mercFL25miA 

DFfl100miA$Whole_weight <- as.numeric(DFfl100miA$Whole_weight)
DFfl100miA$TL <- as.numeric(DFfl100miA$TL)

mercFL100miA <- DFfl100miA %>% 
  group_by(INTSITE,Species) %>% 
  summarise(n = n(), aveWt = mean(Whole_weight, na.rm = TRUE), 
            aveLt = mean(TL, na.rm = TRUE), aveHg = mean(Hg, na.rm = TRUE))

mercFL100miA 

DFfl25miB$Whole_weight <- as.numeric(DFfl25miB$Whole_weight)
DFfl25miB$TL <- as.numeric(DFfl25miB$TL)

mercFL25miB <- DFfl25miB %>% 
  group_by(INTSITE,Species) %>% 
  summarise(n = n(), aveWt = mean(Whole_weight, na.rm = TRUE), 
            aveLt = mean(TL, na.rm = TRUE), aveHg = mean(Hg, na.rm = TRUE))

mercFL25miB 

DFfl100miB$Whole_weight <- as.numeric(DFfl100miB$Whole_weight)
DFfl100miB$TL <- as.numeric(DFfl100miB$TL)

mercFL100miB <- DFfl100miB %>% 
  group_by(INTSITE,Species) %>% 
  summarise(n = n(), aveWt = mean(Whole_weight, na.rm = TRUE), 
            aveLt = mean(TL, na.rm = TRUE), aveHg = mean(Hg, na.rm = TRUE))

mercFL100miB 

#MRIP
landTtimA
landTtimB

mripFLa <- landTtimA %>% 
  group_by(INTSITE,common) %>% 
  summarise(n = n(), landings = sum(landing), biomass = sum(wgt_ab1, na.rm = TRUE))
mripFLa

mripFLb <- landTtimB %>% 
  group_by(INTSITE,common) %>% 
  summarise(n = n(), landings = sum(landing), biomass = sum(wgt_ab1, na.rm = TRUE))
mripFLb
```

Add in NOLA

```{r}
str(DFla25miA)

mercLA25miA <- DFla25miA %>% 
  group_by(INTSITE,spName) %>% 
  summarise(n = n(), aveWt = mean(aveWt_g, na.rm = TRUE), 
            aveLt = mean(aveLen_cm, na.rm = TRUE), aveHg = mean(HgResult, na.rm = TRUE))
mercLA25miA 

mercLA100miA <- DFla100miA %>% 
  group_by(INTSITE,spName) %>% 
  summarise(n = n(), aveWt = mean(aveWt_g, na.rm = TRUE), 
            aveLt = mean(aveLen_cm, na.rm = TRUE), aveHg = mean(HgResult, na.rm = TRUE))
mercLA100miA 

mercLA25miBA <- DFla25miBA %>% 
  group_by(INTSITE,spName) %>% 
  summarise(n = n(), aveWt = mean(aveWt_g, na.rm = TRUE), 
            aveLt = mean(aveLen_cm, na.rm = TRUE), aveHg = mean(HgResult, na.rm = TRUE))
mercLA25miBA 

mercLA100miBA <- DFla100miBA %>% 
  group_by(INTSITE,spName) %>% 
  summarise(n = n(), aveWt = mean(aveWt_g, na.rm = TRUE), 
            aveLt = mean(aveLen_cm, na.rm = TRUE), aveHg = mean(HgResult, na.rm = TRUE))
mercLA100miBA 

#MRIP
mripLAa <- landOtimA %>% 
  group_by(INTSITE,common) %>% 
  summarise(n = n(), landings = sum(landing), biomass = sum(wgt_ab1, na.rm = TRUE))
mripLAa

mripLAb <- landOtimB %>% 
  group_by(INTSITE,common) %>% 
  summarise(n = n(), landings = sum(landing), biomass = sum(wgt_ab1, na.rm = TRUE))
mripLAb

```
Try to indicate which entries are tested in mrip

```{r}
str(landOtimA)
str(mercLA25miA)
unique(mercLA25miA$spName)

#top sites = 222, 231, 306, 155, 151, within 25 mi
unique(mercLA25miA$INTSITE)
unique(landOtimA$INTSITE)
O222a25 <- subset(mercLA25miA,mercLA25miA$INTSITE == '222')
O231a25 <- subset(mercLA25miA,mercLA25miA$INTSITE == '231')
O306a25 <- subset(mercLA25miA,mercLA25miA$INTSITE == '306')
O155a25 <- subset(mercLA25miA,mercLA25miA$INTSITE == '155')
O151a25 <- subset(mercLA25miA,mercLA25miA$INTSITE == '151')

indLA25a222 <- which((landOtimA$common %in% O222a25$spName) & (landOtimA$INTSITE == '222'))
str(indLA25a222)
landOtimA[indLA25a222,]

landOtimA$testStatus25mi <- rep('NA', nrow(landOtimA))
landOtimA$testStatus25mi[indLA25a222] <- 'Tested'

indLA25a231 <- which((landOtimA$common %in% O231a25$spName) & (landOtimA$INTSITE == '231'))
str(indLA25a231)
landOtimA[indLA25a231,]
landOtimA$testStatus25mi[indLA25a231] <- 'Tested'

indLA25a306 <- which((landOtimA$common %in% O306a25$spName) & (landOtimA$INTSITE == '306'))
str(indLA25a306)
landOtimA[indLA25a306,]
landOtimA$testStatus25mi[indLA25a306] <- 'Tested'

indLA25a155 <- which((landOtimA$common %in% O155a25$spName) & (landOtimA$INTSITE == '155'))
str(indLA25a155)
landOtimA[indLA25a155,]
landOtimA$testStatus25mi[indLA25a155] <- 'Tested'

indLA25a151 <- which((landOtimA$common %in% O151a25$spName) & (landOtimA$INTSITE == '151'))
str(indLA25a151)
landOtimA[indLA25a151,]
landOtimA$testStatus25mi[indLA25a151] <- 'Tested'

landOtimA$testStatus25mi[landOtimA$testStatus25mi %in% 'NA'] <- 'Not Tested'

#top sites = 222, 231, 306, 155, 151, within 100 mi
unique(mercLA100miA$INTSITE)
unique(mercLA100miA$spName)
unique(landOtimA$INTSITE)
O222a100 <- subset(mercLA100miA,mercLA100miA$INTSITE == '222')
O231a100 <- subset(mercLA100miA,mercLA100miA$INTSITE == '231')
O306a100 <- subset(mercLA100miA,mercLA100miA$INTSITE == '306')
O155a100 <- subset(mercLA100miA,mercLA100miA$INTSITE == '155')
O151a100 <- subset(mercLA100miA,mercLA100miA$INTSITE == '151')

indLA100a222 <- which((landOtimA$common %in% O222a100$spName) & (landOtimA$INTSITE == '222'))
str(indLA100a222)
landOtimA[indLA100a222,]

landOtimA$testStatus100mi <- rep('NA', nrow(landOtimA))
landOtimA$testStatus100mi[indLA100a222] <- 'Tested'

indLA100a231 <- which((landOtimA$common %in% O231a100$spName) & (landOtimA$INTSITE == '231'))
str(indLA100a231)
landOtimA[indLA100a231,]
landOtimA$testStatus100mi[indLA100a231] <- 'Tested'

indLA100a306 <- which((landOtimA$common %in% O306a100$spName) & (landOtimA$INTSITE == '306'))
str(indLA100a306)
landOtimA[indLA100a306,]
landOtimA$testStatus100mi[indLA100a306] <- 'Tested'

indLA100a155 <- which((landOtimA$common %in% O155a100$spName) & (landOtimA$INTSITE == '155'))
str(indLA100a155)
landOtimA[indLA100a155,]
landOtimA$testStatus100mi[indLA100a155] <- 'Tested'

indLA100a151 <- which((landOtimA$common %in% O151a100$spName) & (landOtimA$INTSITE == '151'))
str(indLA100a151)
landOtimA[indLA100a151,]
landOtimA$testStatus100mi[indLA100a151] <- 'Tested'

landOtimA$testStatus100mi[landOtimA$testStatus100mi %in% 'NA'] <- 'Not Tested'

landOtimA

LAaProp25mi <- landOtimA %>%
  group_by(INTSITE, testStatus25mi) %>%
  summarise(n_distinct(common), landings = sum(landing), biomass = sum(wgt_ab1))

LAaProp100mi <- landOtimA %>%
  group_by(INTSITE, testStatus100mi) %>%
  summarise(n_distinct(common), landings = sum(landing), biomass = sum(wgt_ab1))

write.csv(LAaProp25mi, "~/FUIteam/PydioData/env/data_outputs/LAaProp25mi.csv")
write.csv(LAaProp100mi, "~/FUIteam/PydioData/env/data_outputs/LAaProp100mi.csv")
```

New Orleans Time Chunk B

```{r}
str(landOtimB)
str(mercLA25miBA)
unique(mercLA25miBA$spName)
str(mercLA25miA)
str(mercLA100miA)
unique(mercLA25miBA$spName)
unique(mercLA100miBA$spName)
unique(landOtimB$common)

#top sites = 222, 159, 306, 3325, 151, within 25 mi
unique(mercLA25miBA$INTSITE)
unique(landOtimB$INTSITE)
O222ba25 <- subset(mercLA25miBA,mercLA25miBA$INTSITE == '222ba')
O3325ba25 <- subset(mercLA25miBA,mercLA25miBA$INTSITE == '3325ba')
O306ba25 <- subset(mercLA25miBA,mercLA25miBA$INTSITE == '306ba')
O159ba25 <- subset(mercLA25miBA,mercLA25miBA$INTSITE == '159ba')
O151ba25 <- subset(mercLA25miBA,mercLA25miBA$INTSITE == '151ba')

indLA25b222 <- which((landOtimB$common %in% O222ba25$spName) & (landOtimB$INTSITE == '222'))
str(indLA25b222)
landOtimB[indLA25b222,]

landOtimB$testStatus25mi <- rep('NA', nrow(landOtimB))
landOtimB$testStatus25mi[indLA25b222] <- 'Tested'

subset(landOtimB, landOtimB$INTSITE == '3325')
indLA25b3325 <- which((landOtimB$common %in% O3325ba25$spName) & (landOtimB$INTSITE == '3325'))
str(indLA25b3325)
landOtimB[indLA25b3325,]
landOtimB$testStatus25mi[indLA25b3325] <- 'Tested'

indLA25b306 <- which((landOtimB$common %in% O306ba25$spName) & (landOtimB$INTSITE == '306'))
str(indLA25b306)
landOtimB[indLA25b306,]
landOtimB$testStatus25mi[indLA25b306] <- 'Tested'

indLA25b159 <- which((landOtimB$common %in% O159ba25$spName) & (landOtimB$INTSITE == '159'))
str(indLA25b159)
landOtimB[indLA25b159,]
landOtimB$testStatus25mi[indLA25b159] <- 'Tested'

indLA25b151 <- which((landOtimB$common %in% O151ba25$spName) & (landOtimB$INTSITE == '151'))
str(indLA25b151)
landOtimB[indLA25b151,]
landOtimB$testStatus25mi[indLA25b151] <- 'Tested'

landOtimB$testStatus25mi[landOtimB$testStatus25mi %in% 'NA'] <- 'Not Tested'

#top sites = 222, 159, 306, 3325, 151, within 100 mi
unique(mercLA100miBA$INTSITE)
str(mercLA25miBA)
unique(mercLA100miBA$spName)
unique(landOtimB$INTSITE)

O222ba100 <- subset(mercLA100miBA,mercLA100miBA$INTSITE == '222ba')
O3325ba100 <- subset(mercLA100miBA,mercLA100miBA$INTSITE == '3325ba')
O306ba100 <- subset(mercLA100miBA,mercLA100miBA$INTSITE == '306ba')
O159ba100 <- subset(mercLA100miBA,mercLA100miBA$INTSITE == '159ba')
O151ba100 <- subset(mercLA100miBA,mercLA100miBA$INTSITE == '151ba')

indLA100b222 <- which((landOtimB$common %in% O222ba100$spName) & (landOtimB$INTSITE == '222'))
str(indLA100b222)
landOtimB[indLA100b222,]

landOtimB$testStatus100mi <- rep('NA', nrow(landOtimB))
landOtimB$testStatus100mi[indLA100b222] <- 'Tested'

subset(landOtimB, landOtimB$INTSITE == '3325')
indLA100b3325 <- which((landOtimB$common %in% O3325ba100$spName) & (landOtimB$INTSITE == '3325'))
str(indLA100b3325)
landOtimB[indLA100b3325,]
landOtimB$testStatus100mi[indLA100b3325] <- 'Tested'

indLA100b306 <- which((landOtimB$common %in% O306ba100$spName) & (landOtimB$INTSITE == '306'))
str(indLA100b306)
landOtimB[indLA100b306,]
landOtimB$testStatus100mi[indLA100b306] <- 'Tested'

indLA100b159 <- which((landOtimB$common %in% O159ba100$spName) & (landOtimB$INTSITE == '159'))
str(indLA100b159)
landOtimB[indLA100b159,]
landOtimB$testStatus100mi[indLA100b159] <- 'Tested'

indLA100b151 <- which((landOtimB$common %in% O151ba100$spName) & (landOtimB$INTSITE == '151'))
str(indLA100b151)
landOtimB[indLA100b151,]
landOtimB$testStatus100mi[indLA100b151] <- 'Tested'

landOtimB$testStatus100mi[landOtimB$testStatus100mi %in% 'NA'] <- 'Not Tested'

unique(landOtimB$testStatus100mi)

LAbaProp25mi <- landOtimB %>%
  group_by(INTSITE, testStatus25mi) %>%
  summarise(n_distinct(common), landings = sum(landing), biomass = sum(wgt_ab1))

LAbaProp100mi <- landOtimB %>%
  group_by(INTSITE, testStatus100mi) %>%
  summarise(n_distinct(common), landings = sum(landing), biomass = sum(wgt_ab1))

write.csv(LAbaProp25mi, "~/FUIteam/PydioData/env/data_outputs/LAbaProp25mi.csv")
write.csv(LAbaProp100mi, "~/FUIteam/PydioData/env/data_outputs/LAbaProp100mi.csv")
```

Now onto Florida

```{r}
str(landTtimA)
str(mercFL25miA)
str(mercFL100miA)
unique(mercFL25miA$Species)
unique(mercFL100miA$Species)

#need to convert lower case to upper case for the two dataframes to be able search properly
mercFL25miA$Species <- toupper(mercFL25miA$Species)
mercFL25miA$Species <- trimws(mercFL25miA$Species, which = c("right"), whitespace = "[ \t\r\n]")

mercFL100miA$Species <- toupper(mercFL100miA$Species)
mercFL100miA$Species <- trimws(mercFL100miA$Species, which = c("right"), whitespace = "[ \t\r\n]")

#edit COMMON SNOOK in MRIP data to read SNOOK so they match
landTtimA$common <- gsub("COMMON SNOOK", "SNOOK", landTtimA$common)

#top sites = 770, 769, 632, 615, 742, within 25 mi
unique(mercFL25miA$INTSITE)
unique(landTtimA$INTSITE)
T615a25 <- subset(mercFL25miA,mercFL25miA$INTSITE == '615')
T632a25 <- subset(mercFL25miA,mercFL25miA$INTSITE == '632')
T742a25 <- subset(mercFL25miA,mercFL25miA$INTSITE == '742')
T769a25 <- subset(mercFL25miA,mercFL25miA$INTSITE == '769')
T770a25 <- subset(mercFL25miA,mercFL25miA$INTSITE == '770')

indFL25a615 <- which((landTtimA$common %in% T615a25$Species) & (landTtimA$INTSITE == '615'))
str(indFL25a615)
landTtimA[indFL25a615,]
unique((subset(landTtimA,landTtimA$INTSITE == '615'))$common)
unique(T615a25$Species)

landTtimA$testStatus25mi <- rep('NA', nrow(landTtimA))
landTtimA$testStatus25mi[indFL25a615] <- 'Tested'

indFL25a632 <- which((landTtimA$common %in% T632a25$Species) & (landTtimA$INTSITE == '632'))
str(indFL25a632)
landTtimA[indFL25a632,]
unique(T632a25$Species)
landTtimA$testStatus25mi[indFL25a632] <- 'Tested'

indFL25a742 <- which((landTtimA$common %in% T742a25$Species) & (landTtimA$INTSITE == '742'))
str(indFL25a742)
landTtimA[indFL25a742,]
landTtimA$testStatus25mi[indFL25a742] <- 'Tested'

indFL25a769 <- which((landTtimA$common %in% T769a25$Species) & (landTtimA$INTSITE == '769'))
str(indFL25a769)
landTtimA[indFL25a769,]
landTtimA$testStatus25mi[indFL25a769] <- 'Tested'

indFL25a770 <- which((landTtimA$common %in% T770a25$Species) & (landTtimA$INTSITE == '770'))
str(indFL25a770)
landTtimA[indFL25a770,]
landTtimA$testStatus25mi[indFL25a770] <- 'Tested'

landTtimA$testStatus25mi[landTtimA$testStatus25mi %in% 'NA'] <- 'Not Tested'
```

100 mi chunk for FL, time frame A

```{r}
#top sites = 770, 769, 632, 615, 742, within 100 mi
unique(mercFL100miA$INTSITE)
unique(landTtimA$INTSITE)
T615a100 <- subset(mercFL100miA,mercFL100miA$INTSITE == '615')
T632a100 <- subset(mercFL100miA,mercFL100miA$INTSITE == '632')
T742a100 <- subset(mercFL100miA,mercFL100miA$INTSITE == '742')
T769a100 <- subset(mercFL100miA,mercFL100miA$INTSITE == '769')
T770a100 <- subset(mercFL100miA,mercFL100miA$INTSITE == '770')

indFL100a615 <- which((landTtimA$common %in% T615a100$Species) & (landTtimA$INTSITE == '615'))
str(indFL100a615)
landTtimA[indFL100a615,]
unique((subset(landTtimA,landTtimA$INTSITE == '615'))$common)
unique(T615a100$Species)

landTtimA$testStatus100mi <- rep('NA', nrow(landTtimA))
landTtimA$testStatus100mi[indFL100a615] <- 'Tested'

indFL100a632 <- which((landTtimA$common %in% T632a100$Species) & (landTtimA$INTSITE == '632'))
str(indFL100a632)
landTtimA[indFL100a632,]
unique(T632a100$Species)
landTtimA$testStatus100mi[indFL100a632] <- 'Tested'

indFL100a742 <- which((landTtimA$common %in% T742a100$Species) & (landTtimA$INTSITE == '742'))
str(indFL100a742)
landTtimA[indFL100a742,]
landTtimA$testStatus100mi[indFL100a742] <- 'Tested'

indFL100a769 <- which((landTtimA$common %in% T769a100$Species) & (landTtimA$INTSITE == '769'))
str(indFL100a769)
landTtimA[indFL100a769,]
landTtimA$testStatus100mi[indFL100a769] <- 'Tested'

indFL100a770 <- which((landTtimA$common %in% T770a100$Species) & (landTtimA$INTSITE == '770'))
str(indFL100a770)
landTtimA[indFL100a770,]
landTtimA$testStatus100mi[indFL100a770] <- 'Tested'

landTtimA$testStatus100mi[landTtimA$testStatus100mi %in% 'NA'] <- 'Not Tested'

FLaProp25mi <- landTtimA %>%
  group_by(INTSITE, testStatus25mi) %>%
  summarise(n_distinct(common), landings = sum(landing), biomass = sum(wgt_ab1))

FLaProp100mi <- landTtimA %>%
  group_by(INTSITE, testStatus100mi) %>%
  summarise(n_distinct(common), landings = sum(landing), biomass = sum(wgt_ab1))

write.csv(FLaProp25mi, "~/FUIteam/PydioData/env/data_outputs/FLaProp25mi.csv")
write.csv(FLaProp100mi, "~/FUIteam/PydioData/env/data_outputs/FLaProp100mi.csv")
```

Timeframe B, 25 mi

```{r}
str(landTtimB)
str(mercFL25miB)
unique(mercFL25miB$Species)

#need to convert lower case to upper case for the two dataframes to be able search properly
mercFL25miB$Species <- toupper(mercFL25miB$Species)
mercFL25miB$Species <- trimws(mercFL25miB$Species, which = c("right"), whitespace = "[ \t\r\n]")

mercFL100miB$Species <- toupper(mercFL100miB$Species)
mercFL100miB$Species <- trimws(mercFL100miB$Species, which = c("right"), whitespace = "[ \t\r\n]")

#edit COMMON SNOOK in MRIP data to read SNOOK so they match
landTtimB$common <- gsub("COMMON SNOOK", "SNOOK", landTtimB$common)

#top sites = 770, 632, 3802, 769, 614, within 25 mi
unique(mercFL25miB$INTSITE)
unique(landTtimB$INTSITE)
T614b25 <- subset(mercFL25miB,mercFL25miB$INTSITE == '614b')
T632b25 <- subset(mercFL25miB,mercFL25miB$INTSITE == '632b')
T3802b25 <- subset(mercFL25miB,mercFL25miB$INTSITE == '3802b')
T769b25 <- subset(mercFL25miB,mercFL25miB$INTSITE == '769b')
T770b25 <- subset(mercFL25miB,mercFL25miB$INTSITE == '770b')

indFL25a614 <- which((landTtimB$common %in% T614b25$Species) & (landTtimB$INTSITE == '614'))
str(indFL25a614)
landTtimB[indFL25a614,]
unique((subset(landTtimB,landTtimB$INTSITE == '614'))$common)
unique(T614b25$Species)

landTtimB$testStatus25mi <- rep('NA', nrow(landTtimB))
landTtimB$testStatus25mi[indFL25a614] <- 'Tested'

indFL25a632 <- which((landTtimB$common %in% T632b25$Species) & (landTtimB$INTSITE == '632'))
str(indFL25a632)
landTtimB[indFL25a632,]
unique(T632b25$Species)
landTtimB$testStatus25mi[indFL25a632] <- 'Tested'

indFL25a3802 <- which((landTtimB$common %in% T3802b25$Species) & (landTtimB$INTSITE == '3802'))
str(indFL25a3802)
landTtimB[indFL25a3802,]
landTtimB$testStatus25mi[indFL25a3802] <- 'Tested'

indFL25a769 <- which((landTtimB$common %in% T769b25$Species) & (landTtimB$INTSITE == '769'))
str(indFL25a769)
landTtimB[indFL25a769,]
landTtimB$testStatus25mi[indFL25a769] <- 'Tested'

indFL25a770 <- which((landTtimB$common %in% T770b25$Species) & (landTtimB$INTSITE == '770'))
str(indFL25a770)
landTtimB[indFL25a770,]
landTtimB$testStatus25mi[indFL25a770] <- 'Tested'

landTtimB$testStatus25mi[landTtimB$testStatus25mi %in% 'NA'] <- 'Not Tested'
```

now 100 mi, timeframe B

```{r}
#top sites = 770, 632, 3802, 769, 614, within 100 mi
unique(mercFL100miB$INTSITE)
unique(landTtimB$INTSITE)
T614b100 <- subset(mercFL100miB,mercFL100miB$INTSITE == '614b')
T632b100 <- subset(mercFL100miB,mercFL100miB$INTSITE == '632b')
T3802b100 <- subset(mercFL100miB,mercFL100miB$INTSITE == '3802b')
T769b100 <- subset(mercFL100miB,mercFL100miB$INTSITE == '769b')
T770b100 <- subset(mercFL100miB,mercFL100miB$INTSITE == '770b')

indFL100a614 <- which((landTtimB$common %in% T614b100$Species) & (landTtimB$INTSITE == '614'))
str(indFL100a614)
landTtimB[indFL100a614,]
unique((subset(landTtimB,landTtimB$INTSITE == '614'))$common)
unique(T614b100$Species)

landTtimB$testStatus100mi <- rep('NA', nrow(landTtimB))
landTtimB$testStatus100mi[indFL100a614] <- 'Tested'

indFL100a632 <- which((landTtimB$common %in% T632b100$Species) & (landTtimB$INTSITE == '632'))
str(indFL100a632)
landTtimB[indFL100a632,]
unique(T632b100$Species)
landTtimB$testStatus100mi[indFL100a632] <- 'Tested'

indFL100a3802 <- which((landTtimB$common %in% T3802b100$Species) & (landTtimB$INTSITE == '3802'))
str(indFL100a3802)
landTtimB[indFL100a3802,]
landTtimB$testStatus100mi[indFL100a3802] <- 'Tested'

indFL100a769 <- which((landTtimB$common %in% T769b100$Species) & (landTtimB$INTSITE == '769'))
str(indFL100a769)
landTtimB[indFL100a769,]
unique((subset(landTtimB,landTtimB$INTSITE == '769'))$common)
unique(T769b100$Species)
landTtimB$testStatus100mi[indFL100a769] <- 'Tested'

indFL100a770 <- which((landTtimB$common %in% T770b100$Species) & (landTtimB$INTSITE == '770'))
str(indFL100a770)
landTtimB[indFL100a770,]
landTtimB$testStatus100mi[indFL100a770] <- 'Tested'

landTtimB$testStatus100mi[landTtimB$testStatus100mi %in% 'NA'] <- 'Not Tested'

FLbProp25mi <- landTtimB %>%
  group_by(INTSITE, testStatus25mi) %>%
  summarise(n_distinct(common), landings = sum(landing), biomass = sum(wgt_ab1))

FLbProp100mi <- landTtimB %>%
  group_by(INTSITE, testStatus100mi) %>%
  summarise(n_distinct(common), landings = sum(landing), biomass = sum(wgt_ab1))

write.csv(FLbProp25mi, "~/FUIteam/PydioData/env/data_outputs/FLbProp25mi.csv")
write.csv(FLbProp100mi, "~/FUIteam/PydioData/env/data_outputs/FLbProp100mi.csv")
```


Size Comparison
try it out, LA time frame A

```{r, echo = FALSE}

##GO TO NEXT SECTION _ IGNORE THIS ONE
str(DFla100miA)
str(mercLA100miA)
str(landOtimA)



#222, 231, 306, 155, 151,
#wgt, vectors 222
Awgt222mrip <- subset(landOtimA,landOtimA$INTSITE == '222')
Awgt222mripT <- subset(Awgt222mrip,Awgt222mrip$testStatus100mi == 'Tested')
Awgt222merc <- subset(DFla100miA,DFla100miA$INTSITE == '222')
Awgt222mercT <- Awgt222merc[Awgt222merc$spName %in% (unique(Awgt222mripT$common)),]

unique(Awgt222mrip$common)
unique(Awgt222mripT$common)

View(Awgt222mripT)
View(Awgt222merc)
Asub222mrip <- Awgt222mripT[,c(11:12,21)]
Asub222mrip$aveWt_g <- (Awgt222mripT$wgt_ab1/Awgt222mripT$landing)*1000 #to get ave size per fish
Asub222mrip$source <- 'MRIP'

colnames(Asub222mrip) <- c("ZIP", "spName", "aveWt_g","source")

Asub222merc <- Awgt222mercT[,c(10:11)]
Asub222merc$source <- 'MERC'
Asub222merc$ZIP <- 'NA'
Asub222merc <- Asub222merc[,c("ZIP", "spName", "aveWt_g","source")]
unique(Asub222merc$spName)

comp222a <- rbind(Asub222mrip,Asub222merc)

ggplot(comp222a, aes(x=spName, y=aveWt_g, fill = source))  + 
  geom_boxplot() + 
  xlab("Species") + 
  ylab("Average Weight (g)") +
  theme(axis.text.x = element_text(size = 12, face = "bold", angle = 45, hjust = 1),
        axis.text.y = element_text(size = 12, face = "bold"),  
        axis.title.x = element_text(size = 16, face = "plain"),
        axis.title.y = element_text(size = 16, face = "plain")) + 
  theme(legend.text=element_text(size = 12, face = "plain"),
        legend.title=element_text(size = 14, face = "bold"))

library(plyr)
results.222a <-ddply(comp222a,.(spName),function(x) summarize(x,
Pvalue=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$p.value,
Estimate.MERC=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[1],
Estimate.MRIP=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[2]))
results.222a$adjP <- p.adjust(results.222a$Pvalue, method = 'fdr', n = length(results.222a$Pvalue))
results.222a$meanDiff <- (results.222a$Estimate.MERC - results.222a$Estimate.MRIP)
results.222a

#wgt, vectors 231
Awgt231mrip <- subset(landOtimA,landOtimA$INTSITE == '231')
Awgt231mripT <- subset(Awgt231mrip,Awgt231mrip$testStatus100mi == 'Tested')
Awgt231merc <- subset(DFla100miA,DFla100miA$INTSITE == '231')
Awgt231mercT <- Awgt231merc[Awgt231merc$spName %in% (unique(Awgt231mripT$common)),]

unique(Awgt231mrip$common)
unique(Awgt231mripT$common)

Asub231mrip <- Awgt231mripT[,c(11:12,21)]
Asub231mrip$source <- 'MRIP'
colnames(Asub231mrip) <- c("ZIP", "spName", "aveWt_g","source")

Asub231merc <- Awgt231mercT[,c(10:11)]
Asub231merc$source <- 'MERC'
Asub231merc$ZIP <- 'NA'
Asub231merc <- Asub231merc[,c("ZIP", "spName", "aveWt_g","source")]
unique(Asub231merc$spName)

comp231a <- rbind(Asub231mrip,Asub231merc)

ggplot(comp231a, aes(x=spName, y=aveWt_g, fill = source))  + 
  geom_boxplot() + 
  xlab("Species") + 
  ylab("Average Weight (g)") +
  theme(axis.text.x = element_text(size = 12, face = "bold", angle = 45, hjust = 1),
        axis.text.y = element_text(size = 12, face = "bold"),  
        axis.title.x = element_text(size = 16, face = "plain"),
        axis.title.y = element_text(size = 16, face = "plain")) + 
  theme(legend.text=element_text(size = 12, face = "plain"),
        legend.title=element_text(size = 14, face = "bold"))

results.231a <-ddply(comp231a,.(spName),function(x) summarize(x,
Pvalue=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$p.value,
Estimate.MERC=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[1],
Estimate.MRIP=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[2]))
results.231a$adjP <- p.adjust(results.231a$Pvalue, method = 'fdr', n = length(results.231a$Pvalue))
results.231a$meanDiff <- (results.231a$Estimate.MERC - results.231a$Estimate.MRIP)
results.231a

#wgt, vectors 306
Awgt306mrip <- subset(landOtimA,landOtimA$INTSITE == '306')
Awgt306mripT <- subset(Awgt306mrip,Awgt306mrip$testStatus100mi == 'Tested')
Awgt306merc <- subset(DFla100miA,DFla100miA$INTSITE == '306')
Awgt306mercT <- Awgt306merc[Awgt306merc$spName %in% (unique(Awgt306mripT$common)),]

Asub306mrip <- Awgt306mripT[,c(11:12,21)]
Asub306mrip$source <- 'MRIP'
colnames(Asub306mrip) <- c("ZIP", "spName", "aveWt_g","source")

Asub306merc <- Awgt306mercT[,c(10:11)]
Asub306merc$source <- 'MERC'
Asub306merc$ZIP <- 'NA'
Asub306merc <- Asub306merc[,c("ZIP", "spName", "aveWt_g","source")]

comp306a <- rbind(Asub306mrip,Asub306merc)
count(Asub306merc$spName)

ggplot(comp306a, aes(x=spName, y=aveWt_g, fill = source))  + 
  geom_boxplot() + 
  xlab("Species") + 
  ylab("Average Weight (g)") +
  theme(axis.text.x = element_text(size = 12, face = "bold", angle = 45, hjust = 1),
        axis.text.y = element_text(size = 12, face = "bold"),  
        axis.title.x = element_text(size = 16, face = "plain"),
        axis.title.y = element_text(size = 16, face = "plain")) + 
  theme(legend.text=element_text(size = 12, face = "plain"),
        legend.title=element_text(size = 14, face = "bold"))

results.306a <-ddply(comp306a,.(spName),function(x) summarize(x,
Pvalue=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$p.value,
Estimate.MERC=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[1],
Estimate.MRIP=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[2]))
results.306a$adjP <- p.adjust(results.306a$Pvalue, method = 'fdr', n = length(results.306a$Pvalue))
results.306a$meanDiff <- (results.306a$Estimate.MERC - results.306a$Estimate.MRIP)
results.306a

#wgt, vectors 155
Awgt155mrip <- subset(landOtimA,landOtimA$INTSITE == '155')
Awgt155mripT <- subset(Awgt155mrip,Awgt155mrip$testStatus100mi == 'Tested')
Awgt155merc <- subset(DFla100miA,DFla100miA$INTSITE == '155')
Awgt155mercT <- Awgt155merc[Awgt155merc$spName %in% (unique(Awgt155mripT$common)),]

Asub155mrip <- Awgt155mripT[,c(11:12,21)]
Asub155mrip$source <- 'MRIP'
colnames(Asub155mrip) <- c("ZIP", "spName", "aveWt_g","source")

Asub155merc <- Awgt155mercT[,c(10:11)]
Asub155merc$source <- 'MERC'
Asub155merc$ZIP <- 'NA'
Asub155merc <- Asub155merc[,c("ZIP", "spName", "aveWt_g","source")]

comp155a <- rbind(Asub155mrip,Asub155merc)
count(Asub155mrip$spName)

ggplot(comp155a, aes(x=spName, y=aveWt_g, fill = source))  + 
  geom_boxplot() + 
  xlab("Species") + 
  ylab("Average Weight (g)") +
  theme(axis.text.x = element_text(size = 12, face = "bold", angle = 45, hjust = 1),
        axis.text.y = element_text(size = 12, face = "bold"),  
        axis.title.x = element_text(size = 16, face = "plain"),
        axis.title.y = element_text(size = 16, face = "plain")) + 
  theme(legend.text=element_text(size = 12, face = "plain"),
        legend.title=element_text(size = 14, face = "bold"))

results.155a <-ddply(comp155a,.(spName),function(x) summarize(x,
Pvalue=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$p.value,
Estimate.MERC=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[1],
Estimate.MRIP=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[2]))
results.155a$adjP <- p.adjust(results.155a$Pvalue, method = 'fdr', n = length(results.155a$Pvalue))
results.155a$meanDiff <- (results.155a$Estimate.MERC - results.155a$Estimate.MRIP)
results.155a
```

Going to try this a different way, ignoring intsite but also removing duplicate mercury results. Will only use mercury samples from within 100 mi

```{r}
str(DFla100miA)
subDFla100miA <- DFla100miA[,1:21]
str(subDFla100miA)

#calculate ave weight for MRIP
landOtimAwt <- landOtimA
landOtimAwt$aveWt <- (landOtimAwt$wgt_ab1*1000)/landOtimAwt$landing #in g

meltDFla100miA <- subDFla100miA %>% distinct()
str(meltDFla100miA)
unique(meltDFla100miA$spName)

#now compare mrip to merc for time frame A in Louisiana
mripLATestedA <- subset(landOtimAwt,landOtimAwt$testStatus100mi == 'Tested')
mercLAtestA <- meltDFla100miA[meltDFla100miA$spName %in% (unique(mripLATestedA$common)),]
unique(mercLAtestA$spName)

AsubLAmrip <- mripLATestedA[,c(11:12,21)]
AsubLAmrip$source <- 'MRIP'
colnames(AsubLAmrip) <- c("ZIP", "spName", "aveWt_g","source")

AsubLAmerc <- mercLAtestA[,c(10:11)]
AsubLAmerc$source <- 'MERC'
AsubLAmerc$ZIP <- 'NA'
AsubLAmerc <- AsubLAmerc[,c("ZIP", "spName", "aveWt_g","source")]

compLAa <- rbind(AsubLAmrip,AsubLAmerc)

compLAa$aveWt_kg <- compLAa$aveWt_g/1000

ggplot(compLAa, aes(x=spName, y=aveWt_kg, fill = source))  + 
  geom_boxplot() + 
  xlab("Species") + 
  ylab("Average Weight (g)") +
  theme(axis.text.x = element_text(size = 12, face = "bold"),
        axis.text.y = element_text(size = 12, face = "bold"),  
        axis.title.x = element_text(size = 16, face = "plain"),
        axis.title.y = element_text(size = 16, face = "plain")) + 
  theme(legend.text=element_text(size = 12, face = "plain"),
        legend.title=element_text(size = 14, face = "bold")) + coord_flip()

results.LAa <-ddply(compLAa,.(spName),function(x) summarize(x,
Pvalue=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$p.value,
Estimate.MERC=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[1],
Estimate.MRIP=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[2]))
results.LAa$adjP <- p.adjust(results.LAa$Pvalue, method = 'fdr', n = length(results.LAa$Pvalue))
results.LAa$meanDiff <- (results.LAa$Estimate.MERC - results.LAa$Estimate.MRIP)
results.LAa

###timeframe B
landOtimBwt <- landOtimB
landOtimBwt$aveWt <- (landOtimBwt$wgt_ab1*1000)/landOtimBwt$landing #in g

str(DFla100miBA)
subDFla100miB <- DFla100miBA[,1:21]
str(subDFla100miB)

meltDFla100miB <- subDFla100miB %>% distinct()
str(meltDFla100miB)
unique(meltDFla100miB$spName)

#now compare mrip to merc for time frame B in Louisiana
mripLATestedB <- subset(landOtimBwt,landOtimBwt$testStatus100mi == 'Tested')
mercLAtestB <- meltDFla100miB[meltDFla100miB$spName %in% (unique(mripLATestedB$common)),]
unique(mercLAtestB$spName)
str(mripLATestedB)

BsubLAmrip <- mripLATestedB[,c(11:12,20)]
BsubLAmrip$source <- 'MRIP'
colnames(BsubLAmrip) <- c("ZIP", "spName", "aveWt_g","source")

BsubLAmerc <- mercLAtestB[,c(10:11)]
BsubLAmerc$source <- 'MERC'
BsubLAmerc$ZIP <- 'NA'
BsubLAmerc <- BsubLAmerc[,c("ZIP", "spName", "aveWt_g","source")]

compLAb <- rbind(BsubLAmrip,BsubLAmerc)
compLAb$aveWt_kg <- compLAb$aveWt_g/1000

ggplot(compLAb, aes(x=spName, y=aveWt_g, fill = source))  + 
  geom_boxplot() + 
  xlab("Species") + 
  ylab("Average Weight (g)") +
  theme(axis.text.x = element_text(size = 12, face = "bold"),
        axis.text.y = element_text(size = 12, face = "bold"),  
        axis.title.x = element_text(size = 16, face = "plain"),
        axis.title.y = element_text(size = 16, face = "plain")) + 
  theme(legend.text=element_text(size = 12, face = "plain"),
        legend.title=element_text(size = 14, face = "bold"))

results.LAb <-ddply(compLAb,.(spName),function(x) summarize(x,
Pvalue=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$p.value,
Estimate.MERC=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[1],
Estimate.MRIP=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[2]))
results.LAb$adjP <- p.adjust(results.LAb$Pvalue, method = 'fdr', n = length(results.LAb$Pvalue))
results.LAb$meanDiff <- (results.LAb$Estimate.MERC - results.LAb$Estimate.MRIP)
results.LAb
```

On to FLorida!

```{r}
landTtimAwt <- landTtimA
landTtimAwt$aveWt <- (landTtimAwt$wgt_ab1*1000)/landTtimAwt$landing #in g

str(DFfl100miA)
unique(DFfl100miA$INTSITE)
subDFfl100miA <- DFfl100miA[,1:34]
str(subDFfl100miA)

meltDFfl100miA <- subDFfl100miA %>% distinct()
str(meltDFfl100miA)
unique(meltDFfl100miA$Species)

#need to convert lower case to upper case for the two dataframes to be able search properly
meltDFfl100miA$Species <- toupper(meltDFfl100miA$Species)
meltDFfl100miA$Species <- trimws(meltDFfl100miA$Species, which = c("right"), whitespace = "[ \t\r\n]")

#now compare mrip to merc for time frame A in Louisiana
mripFLTestedA <- subset(landTtimAwt,landTtimAwt$testStatus100mi == 'Tested')
mercFLtestA <- meltDFfl100miA[meltDFfl100miA$Species %in% (unique(mripFLTestedA$common)),]
unique(mripFLTestedA$common)
unique(mercFLtestA$Species)

str(mripFLTestedA)
str(mercFLtestA)
mercFLtestA
AsubFLmrip <- mripFLTestedA[,c(11:12,20)]
AsubFLmrip$source <- 'MRIP'
colnames(AsubFLmrip) <- c("ZIP", "spName", "aveWt_g","source")

AsubFLmerc <- mercFLtestA[,c(12,18)]
AsubFLmerc$source <- 'MERC'
AsubFLmerc$ZIP <- 'NA'
AsubFLmerc <- AsubFLmerc[,c("ZIP", "Species", "Whole_weight","source")]
colnames(AsubFLmerc) <- c("ZIP", "spName", "aveWt_g","source")

compFLa <- rbind(AsubFLmrip,AsubFLmerc)

ggplot(compFLa, aes(x=spName, y=aveWt_g, fill = source))  + 
  geom_boxplot() + 
  xlab("Species") + 
  ylab("Average Weight (g)") +
  theme(axis.text.x = element_text(size = 12, face = "bold", angle = 45, hjust = 1),
        axis.text.y = element_text(size = 12, face = "bold"),  
        axis.title.x = element_text(size = 16, face = "plain"),
        axis.title.y = element_text(size = 16, face = "plain")) + 
  theme(legend.text=element_text(size = 12, face = "plain"),
        legend.title=element_text(size = 14, face = "bold"))

#not enough observations of mercury weights to run
results.FLa <-ddply(compFLa,.(spName),function(x) summarize(x,
Pvalue=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$p.value,
Estimate.MERC=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[1],
Estimate.MRIP=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[2]))
results.FLa$adjP <- p.adjust(results.FLa$Pvalue, method = 'fdr', n = length(results.FLa$Pvalue))
results.FLa$meanDiff <- (results.FLa$Estimate.MERC - results.FLa$Estimate.MRIP)
results.FLa

###timeframe B
landTtimBwt <- landTtimB
landTtimBwt$aveWt <- (landTtimBwt$wgt_ab1*1000)/landTtimBwt$landing #in g

str(DFfl100miB)
subDFfl100miB <- DFfl100miB[,1:34]
str(subDFfl100miB)

meltDFfl100miB <- subDFfl100miB %>% distinct()
str(meltDFfl100miB)

#need to convert lower case to upper case for the two dataframes to be able search properly
meltDFfl100miB$Species <- toupper(meltDFfl100miB$Species)
meltDFfl100miB$Species <- trimws(meltDFfl100miB$Species, which = c("right"), whitespace = "[ \t\r\n]")

#now compare mrip to merc for time frame A in Louisiana
mripFLTestedB <- subset(landTtimBwt,landTtimBwt$testStatus100mi == 'Tested')
mercFLtestB <- meltDFfl100miB[meltDFfl100miB$Species %in% (unique(mripFLTestedB$common)),]
unique(mercFLtestB$Species)
str(mripFLTestedB)
unique(meltDFfl100miB$Species)
unique(mripFLTestedB$common)

BsubFLmrip <- mripFLTestedB[,c(11:12,20)]
BsubFLmrip$source <- 'MRIP'
colnames(BsubFLmrip) <- c("ZIP", "spName", "aveWt_g","source")

BsubFLmerc <- mercFLtestB[,c(12,18)]
BsubFLmerc$source <- 'MERC'
BsubFLmerc$ZIP <- 'NA'
BsubFLmerc <- BsubFLmerc[,c("ZIP", "Species", "Whole_weight","source")]
colnames(BsubFLmerc) <- c("ZIP", "spName", "aveWt_g","source")

compFLb <- rbind(BsubFLmrip,BsubFLmerc)

ggplot(compFLb, aes(x=spName, y=aveWt_g, fill = source))  + 
  geom_boxplot() + 
  xlab("Species") + 
  ylab("Average Weight (g)") +
  theme(axis.text.x = element_text(size = 12, face = "bold", angle = 45, hjust = 1),
        axis.text.y = element_text(size = 12, face = "bold"),  
        axis.title.x = element_text(size = 16, face = "plain"),
        axis.title.y = element_text(size = 16, face = "plain")) + 
  theme(legend.text=element_text(size = 12, face = "plain"),
        legend.title=element_text(size = 14, face = "bold"))

#not enough observations
results.FLb <-ddply(compFLb,.(spName),function(x) summarize(x,
Pvalue=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$p.value,
Estimate.MERC=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[1],
Estimate.MRIP=t.test(aveWt_g~source,data=x,na.rm=TRUE,paired=F)$estimate[2]))
results.FLb$adjP <- p.adjust(results.FLb$Pvalue, method = 'fdr', n = length(results.FLb$Pvalue))
results.FLb$meanDiff <- (results.FLb$Estimate.MERC - results.FLb$Estimate.MRIP)
results.FLb
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
