---
title: "Size Exploration"
output: html_notebook
---

#vis of florida sizes by source

```{r}
ggplot(atlSharkT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(blackSharkT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(bonnetT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(crevalleT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point() #ok

ggplot(flPompT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(floundT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(redDrumT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(kingT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(mackT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()#ok

ggplot(seatroutT,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point() #?
```

#vis for NOLA


```{r}
ggplot(redDrumNO,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(blackDrumNO,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(sheepsNO,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(sFlounderNO,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(seatroutNO,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()

ggplot(snapperNO,aes(x=aveLen, y=aveWt, color=source)) +
  geom_point()
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
